TacticToe: Learning to Prove with Tactics

### 2018-02-20 tactictoe_jv.tex
minor fix in diff

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof
construction.
Because validation functions are only important to check the final proof, we
omit them during the description of proof search algorithm. We denote by $t(g)$
the list of goals produced by the application of a tactic $t$ to a goal $g$.

@@

The exploration term is determined by the prior policy and the current policy.
The current policy is calculate from the number of times a node $x$ has been
traversed during node selection, denoted $\mathit{Visit}(x)$.

>>>>

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof
construction.
Because validation functions are only important to check the final proof, we
omit them during the description of the proof search algorithm. We denote by 
$t(g)$ the list of goals produced by the application of a tactic $t$ to a goal 
$g$.

@@

The exploration term is determined by the prior policy and the current policy.
The current policy is calculated from the number of times a node $x$ has been
traversed during node selection, denoted $\mathit{Visit}(x)$.
